%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\clink{\href{https://portabelhealth.com/welcome}{Portabel Health}}} % Organization
    {Junior Developer Intern} % Job title
    {Jan. 2025 - ongoing} % Date(s)
    {Stockholm, Sweden} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Frontend development using Angular}
        \item {Unit testing using Jest}
        \item {Backend development with Java and Spring Boot}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\clink{\href{https://worklife.so}{Worklife}}} % Organization
    {Software Engineer} % Job title
    {Dec. 2021 - Apr. 2023} % Date(s)
    {Dhaka, Bangladesh} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Frontend development using React, Redux, React query, Bootstrap, React router, and MUI}
        \item {Backend development using Django REST framework and PostgreSQL.}
        \item {Testing and bug fixing}
        \item {Project architecture design tasks}
        \item {Research and development tasks}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\clink{\href{https://worklife.so}{Worklife}}} % Organization
    {Software Engineering Intern} % Job title
    {Jun. 2021 - Nov. 2021} % Date(s)
    {Dhaka, Bangladesh} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Linux OS setup}
        \item {Python, JavaScript basic to advanced}
        \item {ReactJS, Django courses, and advanced projects}
        \item {Others: JSON, REST APIs, bug fixing}
        \item {Templates design using HTML, SCSS, and JS}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\clink{\href{https://aml-bubt.github.io/}{Advanced Machine Learning Lab, BUBT}}} % Organization
    {Researcher} % Job title
    {Dec. 2020 - Dec. 2021} % Date(s)
    {Dhaka, Bangladesh} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborate with team-based research tasks}
        \item {Experimented with algorithms and strategies to reduce the current limit of deep learning-based approaches}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
